\section{Biological Correlates}

This section grounds the \MLP{} in neurobiological, metabolic, and psychological evidence by tracing simultaneous flows of information and energy.

\subsection{Neurological Level: Energy, Memory, and Deletion}
\paragraph{Synaptic Plasticity as Physical Information Processing.} Long-term potentiation and depression require ATP for protein synthesis, ion pumping, and vesicle cycling. Forming or updating memory traces constitutes energy-intensive computation. Forgetting is equally vital: synaptic pruning during sleep and rest removes redundant connections, dissipating energy consistent with \landauer{}.

\paragraph{Sleep as a Global Compression--Deletion Cycle.} Wakefulness increases $\uncertainty$ as experiences accumulate. Slow-wave sleep performs downscaling akin to compression; REM sleep supports confidence-gated erasure of emotionally charged memories. Elevated glucose metabolism during REM, despite absent sensory input, is consistent with the energetic expense of deletion.

\paragraph{Neural Entropy and Predictive Efficiency.} EEG and MEG entropy metrics track neural complexity. Adaptive brains exhibit moderate entropy, balancing novelty encoding with coherence. Depression and PTSD show elevated or rigidly low entropy, reflecting failures to maintain the compression--deletion equilibrium predicted by the \MLP{}.

\subsection{Endocrine and Metabolic Level: Physiology of Unresolved Loops}
\paragraph{Cortisol as a Marker of Epistemic Stress.} Cortisol mobilizes glucose in response to uncertainty. Persistent elevation signals a high $\uncertainty/\confidence$ ratio---a pre-deletion state where energy is readied but never released.

\paragraph{Insulin and Fat Storage as Deferred Computation.} Low confidence drives energy hoarding in adipose tissue, analogous to caching unverified data. Safety and predictability lower the buffer, releasing energy for growth and exploration.

\paragraph{Inflammation as Thermodynamic Friction.} Cytokines and oxidative stress accompany prolonged uncertainty. Mitochondria operate inefficiently, dissipating more heat per ATP. Resolution of uncertainty lowers markers such as C-reactive protein (CRP) and interleukin-6 (IL-6).

\subsection{Psychological and Behavioral Level: Confidence, Resolution, and Flow}
\paragraph{Rumination and Cognitive Loops.} Rumination embodies an open computational loop. Repetitive replay consumes energy without compression, increasing metabolic load and stress.

\paragraph{Emotional Resolution as Deletion.} Resolving conflicts signals that the mind has compressed discordant information into a coherent model, allowing deletion and energetic release. Therapeutic modalities can be interpreted as protocols that raise $\confidence$ above the deletion threshold.

\paragraph{Flow and Energetic Efficiency.} Flow states represent near-equilibrium coupling of uncertainty reduction and energy consumption. Prediction errors resolve immediately, $\confidence$ stays high, and metabolic throughput is optimized. Physiological signatures include synchronized oscillations, moderate dopamine, and reduced cortisol.

\subsection{Cross-Scale Coupling}
\begin{table}[h]
  \centering
  \caption{Information operations and energy signatures across scales.}
  \label{tab:scale_coupling}
  \begin{tabular}{llll}
    \toprule
    Scale & Information Operation & Biological Expression & Energy Signature \\
    \midrule
    Cellular & Autophagy, apoptosis & Data deletion & ATP recycling, heat release \\
    Neural & Synaptic pruning & Compression/erasure & High glucose consumption during REM \\
    Endocrine & Hormonal modulation & Uncertainty buffering & Cortisol/insulin dynamics \\
    Behavioral & Decision making & Confidence calibration & Cognitive load vs. clarity \\
    Social & Trust formation & Distributed compression & Energetic efficiency of cooperation \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Integrative Summary}
Neural evidence reveals energy spikes during deletion; metabolic evidence links unresolved uncertainty to stored reserves and inflammation; psychological evidence ties confidence and closure to energetic efficiency. Health and clarity appear as dual expressions of thermodynamic optimization through informational certainty.
