\section{Experimental Design}

We outline four complementary studies to operationalize the \MLP{} across sleep, emotion, cognition, and social coordination.

\subsection{Study A: Sleep Deletion Study}
\textbf{Aim.} Test whether REM energy expenditure scales with daytime informational entropy and predicts next-day metabolic relief.

\textbf{Participants.} $n=48$ healthy adults (18--40).

\textbf{Design.} Within-subject, three counterbalanced conditions across three lab nights: high-entropy day, low-entropy day, and control. Daytime protocols manipulate novelty using probabilistic learning, sequence prediction, and open problems.

\textbf{Measures.} Real-time EEG for wake entropy ($\uncertainty_{\text{day}}$); confidence probes; polysomnography; whole-room calorimetry; optional FDG-PET subset; morning cortisol, HRV, and memory tests.

\textbf{Analyses.} Linear mixed models: $E_{\text{REM}} \sim 1 + \uncertainty_{\text{day}} + (1\mid \text{subject})$; mediation by overnight entropy reduction; exploratory forgetting indices.

\textbf{Falsification.} Null relationship between daytime entropy, REM energy, and next-day relief challenges the sleep-deletion coupling.

\subsection{Study B: Emotional Resolution Metabolic Study}
\textbf{Aim.} Determine whether emotional resolution produces acute energetic release and durable stress reduction.

\textbf{Participants.} $n=60$ adults with a circumscribed unresolved stressor.

\textbf{Design.} Randomized controlled trial comparing a targeted resolution protocol with an active control (supportive counseling).

\textbf{Measures.} Continuous ECG, skin conductance, respiration, indirect calorimetry, dense EEG, micro-phenomenology time-stamps, salivary cortisol, hs-CRP, continuous glucose monitoring, and sleep actigraphy.

\textbf{Outcomes.} Event-aligned HRV increases, skin conductance decreases, VO$_2$ normalization, EEG entropy decreases and coherence increases, followed by 24--48~h cortisol reduction and sleep improvement.

\textbf{Falsification.} Absence of acute physiological inflection points or durable differences relative to control undermines the \MLP{} prediction.

\subsection{Study C: Cognitive Compression and Glucose Efficiency}
\textbf{Aim.} Quantify energy per unit of informational entropy reduced during learning.

\textbf{Participants.} $n=40$ healthy adults.

\textbf{Design.} Within-subject comparison of compressible regularities versus incompressible noise.

\textbf{Measures.} EEG/MEG entropy reduction ($\Delta \uncertainty$), FDG-PET or calibrated fNIRS plus calorimetry, learning curves, confidence calibration.

\textbf{Metric.} Energy-per-bit efficiency $\eta = E_{\text{block}} / \Delta \uncertainty$.

\textbf{Prediction.} Lower $\eta$ for compressible structure and steeper $\eta$ decline as confidence rises.

\textbf{Falsification.} Equivalent or worse efficiency for compressible conditions, or independence from confidence, contradicts the hypothesis.

\subsection{Study D: Social Trust and Collective Energy}
\textbf{Aim.} Test whether trust reduces redundant verification and energy expenditure in groups.

\textbf{Participants.} Twenty-four teams of five.

\textbf{Design.} Teams randomized to trust-priming versus neutral conditions before cooperative planning tasks with hidden information.

\textbf{Measures.} Group calorimetry or wearable proxies, hyperscanning fNIRS, communication entropy, decision accuracy and latency.

\textbf{Prediction.} Trust-primed groups display lower redundancy, reduced energy per decision, and higher inter-brain coherence.

\textbf{Falsification.} No trust-related differences after controlling for skill implies social confidence may not map to energetic efficiency.

\subsection{Shared Elements}
\begin{itemize}
  \item \textbf{Power and statistics}: Medium effects detectable with $n \approx 40$--60 per study arm; simulations for precision.
  \item \textbf{Primary estimands}: Slopes of energy versus entropy reduction ($\partial E / \partial \Delta \uncertainty$) and confidence-mediated pathways.
  \item \textbf{Preregistration}: Hypotheses, analyses, and exclusion criteria pre-specified; tasks and code shared openly.
  \item \textbf{Ethics}: Minimal risk protocols with monitoring, PET limited to subsets under radiological oversight.
  \item \textbf{Falsifiers}: Absence of monotonic relationships among uncertainty, confidence, and energy at any scale constrains the \MLP{} scope.
\end{itemize}
