\section{Conceptual Framework: The \MLP}

\subsection{Definition}
We define the \MLP{} via the energetic cost of deleting uncertainty in biological systems:
\begin{equation}
  \energydelete = k_B T \ln 2 \cdot f(\uncertainty, \confidence, \metabolic),
\end{equation}
where $\uncertainty$ denotes residual informational entropy, $\confidence$ is epistemic trust in the fidelity of an updated predictive model, and $\metabolic$ captures available free energy. We specify
\begin{equation}
  f(\uncertainty, \confidence, \metabolic) = \frac{\uncertainty}{\confidence} \cdot g(\metabolic),
\end{equation}
so confident systems ($\confidence \gg \uncertainty$) delete obsolete information at lower energetic cost, while uncertain systems incur higher barriers to letting go.

\subsection{Cognitive--Thermodynamic Loop}
The brain--body system operates as a closed-loop thermodynamic information engine:
\begin{enumerate}[label=(\roman*)]
  \item \textbf{Perception}: Novel data increase $\uncertainty$.
  \item \textbf{Learning}: Compression decreases $\uncertainty$ and increases $\confidence$.
  \item \textbf{Deletion}: When $\confidence$ exceeds a threshold $\confidence_c$, energy $\energydelete$ is expended to erase obsolete representations.
  \item \textbf{Metabolic Update}: Dissipated energy frees neural and metabolic capacity for new learning.
\end{enumerate}
Stalled loops---due to chronic stress or ambiguity---prevent confident deletion, yielding persistent activation, elevated cortisol, and stored energy.

\subsection{Energy Storage as Deferred Computation}
Energy reserves function as deferred computation under high uncertainty. When deletion is unsafe, biological systems hoard energy analogously to redundant data storage. Table~\ref{tab:states} summarizes the mapping.
\begin{table}[h]
  \centering
  \caption{Informational states and physiological correlates.}
  \label{tab:states}
  \begin{tabular}{lll}
    \toprule
    Informational State & Physiological Correlate & Description \\
    \midrule
    Unresolved loop & Chronic stress & Recurrent prediction errors; sustained cortisol \\
    Redundant memory & Energy storage & Fat accumulation as ``uncertainty buffer'' \\
    Confident compression & Homeostasis & Balanced energy allocation and predictive trust \\
    Excessive deletion & Burnout & Overconfidence with underpreparedness \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{The Confidence Threshold and Deletion Barrier}
We frame the deletion barrier as
\begin{equation}
  \entropydelete = k_B T \ln 2 \cdot \frac{\uncertainty}{\confidence}.
\end{equation}
Deletion proceeds when available metabolic energy $\metabolic_{\text{free}}$ exceeds this barrier:
\begin{equation}
  \metabolic_{\text{free}} \geq \entropydelete.
\end{equation}
Confidence acts analogously to a catalyst: increasing $\confidence$ lowers the barrier, enabling irreversible transformation.

\subsection{Cognitive Homeostasis as Entropy--Energy Equilibrium}
The organism seeks dynamic equilibrium
\begin{equation}
  \frac{\mathrm{d}\uncertainty}{\mathrm{d}t} + \frac{\mathrm{d}\metabolic}{\mathrm{d}t} \approx 0.
\end{equation}
Increases in uncertainty demand metabolic expenditure; decreasing uncertainty via learning and deletion releases energy.

\subsection{Systemic Integration}
Across scales, the \MLP{} binds processes:
\begin{itemize}
  \item \textbf{Cellular}: Autophagy and apoptosis as data deletion with heat dissipation.
  \item \textbf{Neural}: Synaptic pruning and memory consolidation consuming glucose.
  \item \textbf{Emotional}: Resolution and forgiveness modulating cortisol and energetic release.
  \item \textbf{Systemic}: Metabolism and immune response buffering against uncertainty.
  \item \textbf{Social}: Trust loops enabling distributed compression and energetic efficiency.
\end{itemize}

\subsection{Implications}
Key implications include:
\begin{itemize}
  \item Emotions regulate deletion thresholds by signaling when erasure is safe.
  \item Learning fatigue reflects accumulated deletion costs near the \landauer{} bound.
  \item Trauma and chronic stress manifest as high-entropy attractors with blocked deletion.
  \item Therapeutic resolution restores epistemic trust, lowering deletion barriers.
  \item Synthetic cognition could leverage confidence-based deletion for energetic regulation.
\end{itemize}

\subsection{Conceptual Summary}
Table~\ref{tab:concept_summary} summarizes the mapping between information-theoretic expressions and biological manifestations.
\begin{table}[h]
  \centering
  \caption{Conceptual summary of the \MLP{}.}
  \label{tab:concept_summary}
  \begin{tabular}{lll}
    \toprule
    Concept & Information-Theoretic Expression & Biological Expression \\
    \midrule
    Learning & Compression of data & Neural encoding \\
    Deletion & Irreversible erasure & Synaptic pruning, emotional release \\
    Confidence & Predictive fidelity & Trust, coherence, faith \\
    Energy & Substrate of computation & Metabolic ATP flow \\
    Disease & Failure of safe deletion & Chronic uncertainty, energy storage \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Synthesis}
The \MLP{} unites cognitive, emotional, and metabolic processes under a single physical law: the cost of learning and the discomfort of letting go are expressions of the same thermodynamic constraint. Learning consumes energy to compress uncertainty; confident deletion dissipates energy to achieve clarity. Adaptation emerges from the oscillation between these poles.
