\section{Protocol: Run the \MLP{} Human Experiment}

\subsection{Step 1: Pick a Loop}
Choose a cognitive or emotional loop that keeps draining attention. Write it as a single sentence labelled ``Open Loop.''

\subsection{Step 2: Baseline Energy Check}
\begin{itemize}
  \item Subjective: rate current energy from 0--100.
  \item Optional sensors: note resting heart rate, HRV, breath rate, or smartwatch stress scores.
\end{itemize}

\subsection{Step 3: Compression Session}
Spend 10--20 minutes translating the loop into the shortest honest model. Journal, record audio, or talk with a collaborator. Aim for the minimal algorithm that still predicts your reaction.

\subsection{Step 4: Confidence Probe}
Assess trust in the new model on a 0--100 scale. If $<70$, repeat compression. If $\geq 70$, proceed.

\subsection{Step 5: Deletion Ritual}
Perform a physical, irreversible act to mark the deletion:
\begin{itemize}
  \item Burn or shred the draft.
  \item Delete the redundant file and replace it with a one-line summary.
  \item Exhale slowly while naming the lesson out loud.
\end{itemize}

\subsection{Step 6: Post-Deletion Measures}
Capture immediate and delayed shifts:
\begin{itemize}
  \item Energy rating now, plus 12-hour and 24-hour follow-ups.
  \item Optional sensor readings (HR, HRV, sleep score).
  \item Physical sensations: warmth, calm, tearfulness, hunger, etc.
\end{itemize}

\subsection{Step 7: Log the Pattern}
Document the sequence: loop, compression, confidence, deletion, energy change. A sample schema appears in Table~\ref{tab:log_schema}.

\begin{table}[h]
  \centering
  \caption{Suggested logging template for memetic self-experiments.}
  \label{tab:log_schema}
  \begin{tabular}{llllll}
    \toprule
    Loop & Confidence Pre & Confidence Post & Energy Pre & Energy Post & Notes \\
    \midrule
    Decision backlog & 32 & 84 & 41 & 67 & ``Warm chest, slept 90~min.'' \\
    \bottomrule
  \end{tabular}
\end{table}
